A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-15 6_validation.tex
lil edits to validation

\section{Validation}
In order to test our framework we have assembled a data set of various types of 3D model, ranging over various applications and various types of geometry.
The dataset is described in detail in the accompanying data in Appendix~\ref{dataset}.
We sliced all models in the dataset and selected 300 random slices from the total set of slices.

@@

\begin{figure*}
\centering
\setlength{\figheight}{0.2\textwidth}
\setlength{\figwidth}{0.24\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/computime2.pdf}
%\includegraphics[width=\figwidth]{sources/validation/computime2.pdf}
\caption{Computation time and target vertex count for the full dataset}
\label{computime}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/overunderfill.pdf}
%\includegraphics[width=\figwidth]{sources/validation/overunderfill.pdf}
\caption{Total over and underfill area}
\label{over_underfill}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/widthHistogram.pdf}
%\includegraphics[width=\figwidth]{sources/validation/widthHistogram.pdf}
\caption{Relative frequency of extrusion widths}
\label{widthHistogram}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/smoothness.pdf}
%\includegraphics[width=\figwidth]{sources/validation/smoothness.pdf}
\caption{Frequency of angles between consecutive segments}
\label{smoothness}
\end{subfigure}
\caption{Results of computational analysis of the results from applying the naive method and various beading strategies using our framework to the dataset.}
\end{figure*}

@@

\subsection{Experimentation}
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs linear advance~\cite{tronvoll2019investigating}: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the extruder and the nozzle so that we can realize accurate adaptive deposition width control.
We set the prefered width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.

>>>>

\section{Validation}
In order to test our framework we have assembled a data set of various types of 3D model, ranging over various applications and various types of geometry.
The dataset is described in detail in the accompanying data in Appendix~\ref{dataset}.
We sliced all models in the dataset and selected 300 random slices from the total set of slices for thorough analysis.
We generated the toolpaths on these 300 outline shapes using the naive technique as implemented by Clipper and compare it to the constant bead count strategy with a bead count of $C=4$, the centered beading strategy, the evenly distributed and the inward distributed beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.

@@

\begin{figure*}
\centering
\setlength{\figheight}{0.2\textwidth}
\setlength{\figwidth}{0.24\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/computime2.pdf}
%\includegraphics[width=\figwidth]{sources/validation/computime2.pdf}
\caption{Computation time and target vertex count for the full dataset}
\label{computime}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/overunderfill.pdf}
%\includegraphics[width=\figwidth]{sources/validation/overunderfill.pdf}
\caption{Total over and underfill area}
\label{over_underfill}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/widthHistogram.pdf}
%\includegraphics[width=\figwidth]{sources/validation/widthHistogram.pdf}
\caption{Relative frequency of extrusion widths}
\label{widthHistogram}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/smoothness.pdf}
%\includegraphics[width=\figwidth]{sources/validation/smoothness.pdf}
\caption{Frequency of angles between consecutive segments}
\label{smoothness}
\end{subfigure}
\caption{
Results of computational analysis of the results from applying the naive method and various beading strategies using our framework to the dataset.
Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
}
\end{figure*}

@@

\subsection{Experimentation}
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the extruder and the nozzle so that we can realize accurate adaptive deposition width control.\cite{tronvoll2019investigating}
We set the prefered width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.

### 2019-08-15 8_discussion.tex
lil edits to validation

\subsection{Computation time}
Algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
The number of elements in the trapezoidation is linear in the number of elements in the VD
and all of the stages of our framework are also linear in the number of elements in the skeleton,
so the total running time of our algorithm is $O(n \log n)$.

>>>>

\subsection{Computation time}
The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
The number of elements in the trapezoidation is linear in the number of elements in the VD
and all of the stages of our framework are also linear in the number of elements in the skeleton,
so the total running time of our algorithm is $O(n \log n)$.
